Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-06 ms/manuscript.Rmd
Update MS

Characterizing the spatial distribution of biodiversity is a major goal of evolutionary biology for two reasons: to understand the processes generating it, and to conserve it. The vast majority of studies seeking to understand the spatial distribution of biodiversity focus on species richness. For example, hotspots, or areas of exceptionally high richness, have received particular attention, resulting in a widely-recognized set of 34 terrestrial hotspots and motivating conservation strategies to preserve them. However, richness alone cannot provide a complete picture of biodiversity. All organisms are related by descent from a common ancestor, and these evolutionary relationships must be taken into account to obtain a full understanding of biodiversity.

>>>>

Characterizing the spatial distribution of biodiversity is a major goal of evolutionary biology with two equally important aspects: to understand the processes generating it, and to conserve it. The vast majority of studies seeking to understand the spatial distribution of biodiversity focus on species richness. Hotspots, or areas of exceptionally high richness, have received particular attention, resulting in a widely-recognized set of 34 terrestrial hotspots and motivating conservation strategies to preserve them. However, richness alone cannot provide a complete picture of biodiversity. All organisms are related by descent from a common ancestor, and these evolutionary relationships must be taken into account to obtain a full understanding of biodiversity.
